---
title: "Cyclictic Bike Sharing"
author: "Diji"
date: "12/19/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Business task 
The current primary goal of the company is to maximize the number of annual memberships.To facilitate this process, the marketing teams would like the following three questions answered: 

- How do annual members and casual riders use Cyclistic bikes differently?
- Why would casual riders buy Cyclistic annual memberships?
- How can Cyclistic use digital media to influence casual riders to become members?

# Data Sources
The data was downloaded from this link [here](https://divvy-tripdata.s3.amazonaws.com/index.html), and is the file that was updated on Dec 8, 2021. The data was made available by Motivate International Inc. 

# Analysis 

```{r}
# Import the packages 


```


```{r include=FALSE}
# Import the data 
bike_trips <- fread()
```


# Summary 


# Visualizations and key findings 


# Recommendations 